\Large \bf Traffic Sign Classification

### 2017-12-19 paper/main.tex
Finished second draft

Efficient and accurate classification of traffic signs constitutes an interesting computer vision problem with a high degree of real-world relevance. Traffic sign recognition is necessary for the development of autonomous vehicles and driver assistance systems, which must be able to correctly detect and classify traffic signs in real-time under varying conditions. As such, traffic sign classification has enjoyed significant recent attention, and current techniques are able to meet or surpass human performance in publicly available data sets. Here, I compare successful approaches to traffic sign classification and present the performance of a traffic sign classifier based on a convolutional neural network.

@@

Support vector machines (SVMs) are binary linear classifiers designed to find the best separation between two classes based on a training data set. Like LDA implementations, SVMs can be used to produce non-linear and higher dimensional classifiers necessary for tasks such as traffic sign recognition \cite{mathias_traffic_2013}. SVM-based classifiers perform marginally worse on the GTSRB data set than LDA implementations, with the highest scoring solution correctly classifying 94.23 \% of examples in the training set \cite{mathias_traffic_2013}. Moreover, the time needed to train and test examples using SVMs is highly dependent on the features used, with high-performing implementations based on HOG features requiring upwards of 15 hours to train, though more efficient implementations require on the order of minutes to train and test on the complete GTSRB data set \cite{mathias_traffic_2013, stallkamp_german_2011}.

Overall, SVMs seem to exist in a ``worst of both worlds'' between neural networks and LDA implementations, exhibiting comparatively low correct classification rates at the expense of time intensive training and classification. This makes current SVM-based traffic sign classifiers poorly suited for real-world applications, though given that SVM performance is highly dependent on the feature set, it is possible that creating an efficient and performant SVM sign classifier is simply a matter of selecting the right feature set.

@@

Traffic sign classifiers based on CNNs perform well on the GTSRB data set, with the highest performing implementations reaching or exceeding human performance with the highest performing implementations  classifying between 98.31 \% and 99.17 \% of examples correctly. Unfortunately, the accuracy of CNNs comes at the cost of high training times, with training on the GTSRB data set taking on the order of hours and requiring access to powerful hardware \cite{sermanet_convolutional_2012, sermanet_traffic_2011, stallkamp_german_2011, stallkamp_man_2012}.

@@

The accuracy of classification algorithms can be improved considerably through the use of \emph{committees}, which are sets of classifiers that generate results that can then be combined to reduce error due to misclassifications in individual classifiers. The highest performing classifiers entered into the GTSRB competition were comprised of committees based on convolutional neural networks \cite{ciresan_committee_2011, ciresan_multi-column_2012, stallkamp_german_2011, stallkamp_man_2012}. The original design proposed at the initial stage of the competition was built using a combination of CNNs and multi-layer perceptrons. This approached not only outperformed both MLPs and CNNs alone, but was the only classifier to outperform human participants. The authors refined the design to use only committees of CNNs, with the most advanced implementation reaching 99.46 \% accuracy on the GTSRB data set \cite{ciresan_committee_2011, ciresan_multi-column_2012}.

@@

Linear discriminant analysis and support vector machines offer a significant performance advantage over neural networks, but at the cost of some accuracy. Although both LDA and SVM based techniques boast higher than 95 \% accuracy, this may not be acceptable for real-world situations where recognizing and reacting to a sign is critical for passenger safety \cite{}. Moreover, the designers of the GTSRB competition note that some of the human control participants found the interface used to gather human responses was uninituitive and difficult to use \cite{stallkamp_german_2011, stallkamp_man_2012}. As a result, human performance may have been artificially low due to testing conditions, while the nature of the constructed data set was likely advantageous to the classifiers since each test case has a well defined class with none of the ambiguity associated with real-world driving scenarios. Thus, implementations that fail to match human performance in an artificial environment are likely not good candidates for use in real autonomous vehicles or other safety-critical applications.

As hardware continues to become more powerful, computationally expensive classifiers based on committees of neural networks will likely become an even more attractive approach due to their robustness and accuracy. Indeed, advances in powerful, highly parallel embedded components, such as FPGA, are already seeing use in the automotive industry, are already being used in autonomous driving research \cite{fpga, fpga2}.

@@

One solution to this issue is to adopt many different benchmarks, and use classifiers that perform well on all of them. This is solution suits the traffic sign classification problem well, given that different regions have adopted different sets of traffic signs and classifiers need to be trained on data from every region where it is expected to be used. Indeed, a number of public data sets have been released since the GTSRB data set was made public, including the LISA (United States) and BelgiumTS (Belgium) data sets \cite{mathias_traffic_2013, mogelmose_vision-based_2012}. By benchmarking traffic sign classifiers on a diverse set of benchmarks will prevent overfitting and improve generalizability.

@@

The results discussed above demonstrate that even a simple convolutional neural network can obtain reasonable accuracy when trained with a high quality data set. Although I failed to demonstrate any benefit of data augmentation, the success of this technique in past work indicates that this is a failure in my relatively simplistic methodology rather than an issue with the technique itself \cite{ciresan_committee_2011, sermanet_convolutional_2012}. If I were to repeat this experiment again, I would add a more comprehensive set of transformations in computing the augmented data set.

@@

Given the high accuracy of traffic sign classification techniques based on convolutional neural networks, future work should continue to improve the efficiency of these classifiers. Future benchmarks may wish to take efficiency into account when considering the evaluation of techniques, perhaps through a requirement that some throughput must be maintained.

>>>>

Efficient and accurate classification of traffic signs constitutes an interesting computer vision problem with a high degree of real-world relevance. Traffic sign recognition is necessary for the development of autonomous vehicles and driver assistance systems, which must be able to correctly detect and classify traffic signs in real-time under varying conditions. As such, traffic sign classification has enjoyed significant recent attention, and current techniques are able to meet or surpass human performance in publicly available data sets. Here, I compare successful approaches to traffic sign classification and present the performance of a simple traffic sign classifier based on a convolutional neural network.

@@

Support vector machines (SVMs) are binary linear classifiers designed to find the best separation between two classes based on a training data set. Like LDA implementations, SVMs can be used to produce non-linear and higher dimensional classifiers necessary for tasks such as traffic sign recognition \cite{mathias_traffic_2013}. SVM-based classifiers perform marginally worse on the GTSRB data set than LDA implementations, with the highest scoring solution correctly classifying 94.23 \% of examples in the training set \cite{mathias_traffic_2013}. Moreover, the time needed to train and test examples using SVMs is highly dependent on the features used, with high-performing implementations based on HOG features requiring upwards of 15 hours to train, though more efficient implementations require on the order of minutes to train and test on the complete GTSRB data set \cite{stallkamp_german_2011, mathias_traffic_2013}.

Overall, SVMs seem to exist in a ``worst of both worlds'' between neural networks and LDA implementations, exhibiting comparatively low correct classification rates while also incurring the cost of time intensive training and classification. This makes current SVM-based traffic sign classifiers poorly suited for real-world applications, though given that SVM performance is highly dependent on the feature set, it is possible that creating an efficient and performant SVM sign classifier is simply a matter of selecting the right feature set.

@@

Traffic sign classifiers based on CNNs perform well on the GTSRB data set, with the highest performing implementations reaching or exceeding human performance with the highest performing implementations  classifying between 98.31 \% and 99.17 \% of examples correctly. Unfortunately, the accuracy of CNNs comes at the cost of long training times, with training on the GTSRB data set taking on the order of hours and requiring access to powerful hardware \cite{sermanet_convolutional_2012, sermanet_traffic_2011, stallkamp_german_2011, stallkamp_man_2012}.

@@

The accuracy of classification algorithms can be improved considerably through the use of \emph{committees}, which are sets of classifiers that generate results that can then be combined to compensate for error due to misclassifications in individual classifiers. The highest performing classifiers entered into the GTSRB competition were comprised of committees based on convolutional neural networks \cite{ciresan_committee_2011, ciresan_multi-column_2012, stallkamp_german_2011, stallkamp_man_2012}. The original design proposed at the initial stage of the competition was built using a combination of CNNs and multi-layer perceptrons. This approached not only outperformed both MLPs and CNNs alone, but was the only classifier to outperform human participants. The authors refined the design to use only committees of CNNs, with the most advanced implementation reaching 99.46 \% accuracy on the GTSRB data set \cite{ciresan_committee_2011, ciresan_multi-column_2012}.

@@

Linear discriminant analysis and support vector machines can offer a significant advantage in terms of efficiency over neural networks, but at the cost of some accuracy. Although high performing LDA and SVM based techniques boast roughly 95 \% accuracy, this may not be acceptable for real-world situations where recognizing and reacting to a sign is critical for passenger safety. Moreover, the designers of the GTSRB competition note that some of the human control participants found the interface used to gather human responses was uninituitive and difficult to use \cite{stallkamp_german_2011, stallkamp_man_2012}. As a result, human performance may have been artificially low due to testing conditions, while the nature of the constructed data set was likely advantageous to the classifiers since each test case has a well defined class with none of the ambiguity associated with real-world driving scenarios. Thus, implementations that fail to match human performance in an artificial environment are likely not good candidates for use in real autonomous vehicles or other safety-critical applications.

As hardware continues to become more powerful, computationally expensive classifiers based on committees of neural networks will likely become more attractive due to their robustness and accuracy. Indeed, advances in powerful, highly parallel embedded components, such as FPGA, are already seeing use in the automotive industry and in autonomous driving research \cite{fpga, fpga2}.

@@

One solution to this issue is to adopt many different benchmarks, and use classifiers that perform well on all of them. This is solution suits the traffic sign classification problem well, given that different regions have adopted different sets of traffic signs and classifiers need to be trained on data from every region where it is expected to be used. Indeed, a number of public data sets have been released since the GTSRB data set was made public, including the LISA (United States) and BelgiumTS (Belgium) data sets \cite{mathias_traffic_2013, mogelmose_vision-based_2012}. By benchmarking traffic sign classifiers on a diverse set of benchmarks, we may be able to both prevent overfitting and improve generalizability.

@@

The results discussed above demonstrate that even a simple convolutional neural network can obtain reasonable speed and accuracy when trained with a high quality data set. Although I failed to demonstrate any benefit of data augmentation, the success of this technique in past work indicates that this is a failure in my relatively simplistic methodology rather than an issue with the technique itself \cite{ciresan_committee_2011, sermanet_convolutional_2012}. If I were to repeat this experiment again, I would add a more comprehensive set of transformations in computing the augmented data set.

@@

Given the high accuracy of traffic sign classification techniques based on convolutional neural networks, future work should continue to improve the efficiency of these classifiers. Moreover, given the importance of real-time classification, future work investigating the use of neural networks for traffic sign classification should place more emphasis on efficiency. Future benchmarks may wish to take efficiency into account when considering the evaluation of techniques, perhaps by penalizing low throughput or high CPU/GPU usage.
